\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case A1:  Set System Measurement Time}\\
\textbf{Scope:  }Weather Station\\
\textbf{Level:  }Administrator Goal\\
\textbf{Primary Actor:  }Super User (Administrator)\\
\textbf{Scenario:  }None\\
\textbf{Related Use Cases:  }None\\
\textbf{Stakeholders \& Interests:  }
\begin{itemize}
\item Administrator:  Wants to access/change the times when the
Weather Station makes its measurements
\item User:  Wants weather data available at a time frame (like
measured every $x$ minutes and such)
\end{itemize}
\textbf{Preconditions:  }The Weather Station is online and is
periodically measuring the instrumentation.\\
\textbf{Success Guarantees:  }The rate at which the System requests
weather data from the Weather Station is changed.  The System
requests the weather data at the new rate.\\\\ 
\textbf{Main Success Scenario:  }\\
\begin{tabular}{|p{6cm}|p{6cm}|}\hline
\textbf{Super User} & \textbf{System}\\\hline
1.  Requests to change the Measurement Time &\\\hline
& 2.  Asks for Super-User Credentials\\\hline
3.  Enters Admin Name and Admin Password & \\\hline
& 4.  Confirms the credentials\\\hline
& 5.  Prompts Admin to change measuremnt time\\\hline
6.  Enters a new measurement time & \\\hline
& 7.  Prompts Admin to confirm change\\\hline
8.  Confirms the change & \\\hline
& 9.  Changes the measurement time\\\hline
\end{tabular}
\textbf{Extensions:  }\\
4a.  If the System cannot confirm the Admin's credentials, then the
System alerts the requestor, refuses access, and allows the requestor
multiple attempts.\\
8a.  If the Super User cancels the confimation, then the System does
not change the measurement time.\\\\
\textbf{Frequency of Occurrence:  }Almost Continuous\\\\
\textbf{Special Requirements: }
\begin{itemize}
\item The Weather Station as a whole will measure the instruments at
the set rate by the Weather Station itself; this creates a ``request"
time set by the System independent of the Weather Station's
Measuremnt Time.
\end{itemize}
\textbf{Open Issues:  }
\begin{itemize}
\item What units does the Super User enter the Measurement time?
Seconds? Minutes? Hours? some combination of the three?
\item Remember, this is the \underline{time between measurements}. If
the super-user enters 30 seconds, then the System will request the
Weather
Station to make the measurements every 30 seconds, make the
appropriate calculations and send that weather data to the System.
\end{itemize}
\end{document}
